\subsection{Reservoir Compatibility}
With the RC cyborg framework using different reservoirs in the same harness is
made possible, however this requires some modification to the reservoirs
themselves.
As an example we consider the difficulties involved with training the reservoir
computing system on neural networks.
These networks are constantly changing and growing, even small topological
changes may move an important cluster of neurons outside the range of an
electrode.
A possible approach is to use a random boolean network as a stand in reservoir for a
neural culture.
A random boolean network is a graph where each node is assigned a boolean function
of their inbound edges.
Since these nodes will have either the value 1 or 0 we can select a few of them
and let nodes with state 0 act as no activity, and nodes with the value 1 act as
a spiking neuron.
Similarly sensor stimuli can be used to switch input nodes on or off,
``perturbing'' the system.
Note that this is only one of many possible reservoir specific filters as
defined in the RC cyborg framework altering the functionality of the reservoir.
With this translation two very different underlying reservoirs can now be
interacted with using the same input and output, allowing a system to be trained
on different underlying reservoirs while sharing a majority of code.
Simply making the input and output between two reservoirs compatible will of
course not cause them to behave anything like each other.
The problem of utilizing random boolean networks as a viable stand-in for
neurons is very far from being solved, however compatibility is an important
first step.
\subsection{Adaptivity}
In the RC cyborg framework adaptivity and learning is not elaborated on, but
this aspect will become crucial when the implementations mature.
Reservoir computing does not add any constraints on how the task specific
filters should be constructed, thus typically the filters are created using
general purpose machine learning kits.
For reservoirs such as random boolean networks this is a sensible solution,
however for neural networks that evolve, changing their behavior with time the
RC cyborg must be capable of adapting along with the reservoir.
As with reservoir compatibility this is a complex task, but by considering the
learning system to be a part of the RC-cyborg we may lessen the compatibility
gap between different reservoirs.